Attractive people, Attractive jobs 

### 2024-04-04 paper/paper.qmd
Update paper.qmd

library(tidyverse)
library(palmerpenguins)
library(arrow)
library(ggplot2)

@@

@@

Beauty, as the attractiveness, becomes the standard of everything in the modern society as evolving into a global conversation from body shapes, flawless skin to ideal face which influences towards individual and social-cultural perspectives. Theses standards are being as the measurements with ourselves and others. For a long time, attractiveness provides the important aspects of human interaction and shapes the judgement about people as impacting on first impression when meeting the people for the first time and may have the stereotype of what is the person like. Furthermore, these attractiveness of people influence individuals' educations, gender not only viewing the physical shapes. As a result, these types of attractiveness are creating the bias particularly in the employment. The attractive workers earn 10 to 15 percents more than average or low-looking groups [@Chand 2023]. Even in the diverse environmental workforce of the United states, the interplay between personal attractiveness and professional success has deeply connected. The way of attractiveness could shape and lead the outcome of employment has created by the society and raised the interest among scholars, researchers, and generally regarding the impact of those connection [@Ruffle 2014].

@@

## Data Measurement
## Source
## Physical Attractiveness Dataset
## Educational Attractiveness Dataset
## Gender Attractiveness Dataset

>>>>

library(tidyverse)
library(palmerpenguins)
library(arrow)
library(ggplot2)
library(kableExtra)
library(knitr)

@@

#### data parquet####
analysis_data<-read_parquet(here::here("data/analysis_data/analysis_data.parquet"))

@@

Beauty, as the attractiveness, becomes the standard of everything in the modern society as evolving into a global conversation from body shapes, flawless skin to ideal face which influences towards individual and social-cultural perspectives. Theses standards are being as the measurements with ourselves and others. For a long time, attractiveness provides the important aspects of human interaction and shapes the judgement about people as impacting on first impression when meeting the people for the first time and may have the stereotype of what is the person like. Furthermore, these attractiveness of people influence individuals' educations, gender not only viewing the physical shapes. As a result, these types of attractiveness are creating the bias particularly in the employment. The attractive workers earn 10 to 15 percents more than average or low-looking groups [@Chand]. Even in the diverse environmental workforce of the United states, the interplay between personal attractiveness and professional success has deeply connected. The way of attractiveness could shape and lead the outcome of employment has created by the society and raised the interest among scholars, researchers, and generally regarding the impact of those connection [@Ruffle].

@@

## Data Measurement
This paper utilizes based on the R, as the statistical Programming language [@citeR], 
## Source
This dataset collected the information by survey randomly from the United States in 202 published by University of Toronto Dataverse as the part of the paper named "Attractiveness and Attainment: Status, Beauty, and Jobs in China and the United States" to get the data about the attractiveness, gender and employments to compare those variables to present the relationship with the attractiveness and employments.

## Physical Attractiveness Dataset
The physical attractiveness .vs employment dataset, represented below in @tbl-1 is shown the relationship between each variables' physical attractiveness can corresponds with the employments as higher status jobs and lower status jobs. This dataset, published by [
@USA] as filed R Data updated by 2023, collects the information from the workers in the United States with the general survey to figure out the correlation whit the attractiveness and employments and how does each other influencing, particularly, the beauty of physical that most huge part of attractiveness that people will feel or get the impression easily.  
```{r}
#| label: tbl-1
#| tbl-cap: The dataset containing physical attractiveness and the status of employment.
#| echo: false
#| warning: false

head (cleaned_data, 10) |>
  kable(
    col.names = c("higherstatusjob", "lowerstatusjob","highlyattractive", "lessattractive"),
  booktabs = TRUE
  )

## Educational Attractiveness Dataset
The educational attractiveness dataset, showed below in @tbl-2, presents the relationships of educational attractiveness in which the elite university in this paper case to figure out having better status of jobs/hiring come from attractive as educationally. 
```{r}
#| label: tbl-2
#| tbl-cap: The dataset containing educational attractiveness and the status of employment.
#| echo: false
#| warning: false

head (cleaned_data, 10) |>
  kable(
    col.names = c("higheruni", "middleuni","loweruni", "highlyattractive", "lessattractive"),
  booktabs = TRUE
  )

```
## Gender Attractiveness Dataset

```{r}
#| label: tbl-3
#| tbl-cap: The dataset containing gender attractiveness and the status of employment.
#| echo: false
#| warning: false

head (cleaned_data, 10) |>
  kable(
    col.names = c("male", "female", "highlyattractive", "lessattractive"),
  booktabs = TRUE
  )
